Searching 21-cm Absorption Systems in Chinese Radio Telescopes

### 2016-11-19 ms_21cm.tex
sensitivity section

The 21-cm absorption systems are important in the study of the 
distribution, location, temperature and structure of neutral gas,
and the evolution of neutral gas systems and galaxies over
cosmic time scale.
Due to the narrow intrinsic line width, the 21-cm absorption systems
are proposed to be used to directly measure the cosmic acceleration
\citep{2012ApJ...761L..26D,2014PhRvL.113d1303Y}, via the 
Sandage-Loeb (SL) effect \citep{1962ApJ...136..319S,1998ApJ...499L.111L}.
The uncertainties are from the poorly understood neutral hydrogen
clouds. Path finder surveys, taking less than a year, are needed
to improve our understandings of spatial distribution and physical
properties of neutral hydrogen clouds.
This can be done by the Chinese new generation radio telescopes --
Five-hundred-meter Aperture Spherical radio Telescope (FAST)
\citep{2016RaSc...51.1060L} and
Tianlai \citep{2012IJMPS..12..256C}. In the current and near future,
these are the two symbolic modern radio telescopes in China.
The single-dish FAST, like Arecibo\footnote{https://www.naic.edu},
uses its gigantic single dish to achieve ultimate sensitivity, whereas
Tianlai, designed like CHIME\footnote{http://chime.phas.ubc.ca},
has ultra wide field of view per day, by
using its cylindrical reflectors and arrays of receivers to
scan the northern hemisphere of the sky as the Earth turns.

@@

\section{Sensitivity}\label{sec.sensitivity}

NRAO VLA Sky Survey (NVSS)\footnote{http://www.cv.nrao.edu/nvss/}.

Recent studies show that the number density of absorbers to be $\diff N/\diff z\sim 0.45$
\citep{2005ARA&A..43..861W,2007ASSP....3..501Z}.

Recent discoveries of 21-cm absorption systems have about $20\%$ fractional depth
\citep{2015MNRAS.453.1249A,2015MNRAS.453.1268Z}.

@@

>>>>

The 21-cm absorption systems are important in the study of the 
distribution, location, temperature and structure of neutral gas,
and the evolution of neutral gas systems and galaxies over
cosmic time scale.
Due to the narrow intrinsic line width, the 21-cm absorption systems
are proposed to be used to directly measure the cosmic acceleration
\citep{2012ApJ...761L..26D,2014PhRvL.113d1303Y}, via the 
Sandage-Loeb (SL) effect \citep{1962ApJ...136..319S,1998ApJ...499L.111L}.
The uncertainties are from the poorly understood neutral hydrogen
clouds. Path finder surveys, taking less than a year, are needed
to improve our understandings of spatial distribution and physical
properties of neutral hydrogen clouds.
This can be done by the Chinese new generation radio telescopes --
Five-hundred-meter Aperture Spherical radio Telescope (FAST)
\citep{2016RaSc...51.1060L} and
Tianlai \citep{2012IJMPS..12..256C}. In the current and near future,
these are the two symbolic modern radio telescopes in China.
The single-dish FAST, like Arecibo\footnote{https://www.naic.edu},
uses its gigantic single dish to achieve ultimate sensitivity, whereas
Tianlai, designed like CHIME\footnote{http://chime.phas.ubc.ca},
has ultra wide field of view (FoV) per day, by
using its cylindrical reflectors and arrays of receivers to
scan the northern hemisphere of the sky as the Earth turns.

@@

\section{Sensitivity}\label{sec.sensitivity}
To find possible 21-cm absorption systems, radio telescopes
could be devised to scan the radio sources in
NRAO VLA Sky Survey (NVSS)\footnote{http://www.cv.nrao.edu/nvss/}.
If we assume the distributions of radio sources $n_R$ and
{\HI} clouds $n_{\rm \HI}$ are uniform over the sky, then the redshift
distribution of the 21-cm absorption systems $n_{\rm system}$ would be
\begin{equation}
    n_{\rm system}(z)=n_{\rm \HI}(z)\int_z^\infty n_R(z')\diff z'
\end{equation}
regardless of the observation sensitivity,
where $n_R(z)$ is given by equation (26) of \cite{2010A&ARv..18....1D}.
Spacial distribution of {\HI} is poorly understood and is to be
studied in upcoming surveys.
Recent studies show that the number density of
absorbers to be $\diff n_{\rm \HI}/\diff z\sim 0.045$
per line of sight
\citep{2005ARA&A..43..861W,2007ASSP....3..501Z}, so we apply this value
in the following forcast.

Observation sensitivity depends on the background fluxes and foreground
absorptions (current section), as well as telescope configurations and
observation strategies (section \ref{sec.FAST},\ref{sec.Tianlai}).

NVSS contains 2 million sources (with declination $\delta >-40^{\circ}$,
cover 82\% of the sky) stronger than 2.5
mJy at $\nu=$1.4 GHz \citep{1998AJ....115.1693C} and their flux
distribution $n_R(F)$ is given by \cite{1984ApJ...287..461C}.
Redshifted {\HI} clouds absorb lower frequency bands where
the radio sources are typically brighter by $\nu^{-0.7}$
\citep{1998AJ....115.1693C}, or $(1+z_{\rm \HI})^{0.7}$.
The error of the measurement $\Delta F$ is given by
\begin{equation}
    \Delta F={\rm SEFD}/\sqrt{n_{\rm pol}\Delta\nu\Delta t},
\end{equation}
where SEFD is the system equivalent flux density, $n_{\rm pol}$
is the number of polarizations, $\Delta\nu$ is the line width and
$\Delta t$ is the integration time. $\Delta\nu=(u_{\rm width}/c)\nu_{\rm obs}$,
where $u_{\rm width}$ is the equivalent line width of the {\HI}
absorber. The properties of 21-cm absorbers are primarily derived from
followup studies of optical absorbers. The discovery rate from the
cross correlation is a lower bound on the expect number of absorbers,
since high column density systems in the CNM may systematically
obscure potential background optical sources \citep{2014PhRvL.113d1303Y}. There are
only 3 blind radio detections, and a survey may discover more systems
which are optically obscured. They would likely be cold and at high
column density. For sensitivity purposes, we treat all sources as
$u_{\rm width}=2\ {\rm km\ s}^{-1}$
\citep{1982ApJ...259..495W,2005ARA&A..43..861W}.
$\nu_{\rm obs}$ is the observation frequency. For redshifted
21-cm absorption systems, $\nu_{\rm obs}=1420\ {\rm MHz}/(1+z_{\rm \HI})$.
The integration time $\Delta t=(n_{\rm obs}\times 24\ {\rm h})\tau$,
where $n_{\rm obs}$ is the number of days an object is scanned,
and $\tau=\lambda/2\pi D\cos\delta$ is the fractional time the object
transits the FoV ($\lambda_{\rm obs}\ll D$ or $\delta\nrightarrow\pi/2$).
For 21-cm absorption systems $\lambda_{\rm obs}=21\ {\rm cm}\times (1+z_{\rm obs})$.

In the forecast we count $>10\sigma$ detections, i.e., the absorption
line depth is at least $10\Delta F$. The optical depth of {\HI} absorbers
are also poorly understood. Recent discoveries of 21-cm absorption systems
have about $r=20\%$ fractional depth \citep{2015MNRAS.453.1249A,2015MNRAS.453.1268Z},
and we apply this value. Thus, all systems with $rF>10\Delta F$ are counted.

@@

Different declinations have different SEFD.
